\toolname: file-based localization of numerical perturbations in data analysis pipelines

### 2020-04-14 paper.tex
fix fig.3

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. \note{Greg}{clarify why many processes don't appear in the graph as shown} \tristan{Ali, 
do you pre-process the reprozip trace to remove some processes, or does the figure show all the processes in this trace?}
\note{Ali}{It only shows processes that belong to the pipeline (e.g. /usr/local/src/freesurfer/) 
by making a query on the traced DB file. 
We exclude processes like [cp, awk, sed, tee, date\dots]. \tristan{Several points here: (1) freesurfer is obviously not used in this example, so what filtering was actually done? (2) where is this implemented in the code? (3) 
how do you know that you're not breaking the graph by removing these processes?}}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline. \tristan{Ali, the process tree needs to be in dashed and the file
    dependencies in plain.}}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}

>>>>

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. \note{Greg}{clarify why many processes don't appear in the graph as shown} \tristan{Ali, 
do you pre-process the reprozip trace to remove some processes, or does the figure show all the processes in this trace?}
\note{Ali}{It only shows processes that belong to the pipeline (e.g. /usr/local/src/freesurfer/) 
by making a query on the traced DB file. 
We exclude processes like [cp, awk, sed, tee, date\dots]. \tristan{Several points here: (1) freesurfer is obviously not used in this example, so what filtering was actually done? (2) where is this implemented in the code? (3) 
how do you know that you're not breaking the graph by removing these processes?}}
\note{Ali}{In fact, I excluded processes in /usr/bin/ like [cp, sed, awk, tee, ...] in \emph{get\_processes\_list} function in \emph{auto\_spot.py} script. These processes will not affect the outputs as the results are shown. 
Spot will stop the procedure of labeling if any excluded processes create differences as it cannot labels included processed that read and write files with differences. It didn't happen in my experiments.
}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline.}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}
